01_LH-SIP_Data_Reduction

### 2022-11-28 01_LH-SIP_Data_Reduction.Rmd
added SE of IRMS at t = 0

# Cache the zero-timepoint dataframe
zero_peaks_averaged %>% 
  openxlsx::write.xlsx(
    file.path("cache", 
              "IRMS", 
              "zero_peaks_averaged.xlsx"),
    overwrite = TRUE)

# This is the dataset we will use for generation time calculations
peaks_mapped_with_zeros <- 
  peaks_mapped_mc %>%
  left_join(
    zero_peaks_averaged,
    by = c("soil_id", "compound")
  )
stopifnot(nrow(peaks_mapped_with_zeros) == nrow(peaks_mapped))

@@

>>>>

# Cache the zero-timepoint dataframe
zero_peaks_averaged %>% 
  openxlsx::write.xlsx(
    file.path("cache", 
              "zero_peaks_averaged.xlsx"),
    overwrite = TRUE)

# This is the dataset we will use for generation time calculations
peaks_mapped_with_zeros <- 
  peaks_mapped_mc %>%
  left_join(
    zero_peaks_averaged,
    by = c("soil_id", "compound")
  )
stopifnot(nrow(peaks_mapped_with_zeros) == nrow(peaks_mapped_mc))

@@

# Standard Error of IRMS measurements at time zero
saveRDS(sF_0,
        file = "cache/sF_0.RDS")
